\textsf{Are large language models superhuman chemists?}

### 2024-03-24 src/tex/ms.tex
review curation workflow
reviewed manually curated categories

To ensure that the questions do not enter a training dataset we use the same canary string as the Big Bench project.
This requires that \Gls{llm} developers filter their training dataset for this canary string.\autocite{openai2024gpt4, srivastava2022beyond}

@@

\subparagraph{Combustion engineering}
\variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} questions are based on master student examination papers at the University of Magdeburg (Germany). 
They explore topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nanomaterials}
\variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt}  questions are based on exercises in a seminar conducted at the University of Jena (Germany), delving into topics concerning functional materials and nanomaterials, exploring their properties and applications.

@@

\subparagraph{International Chemical Olympiad}
\variable{output/question_count_per_dir/json_file_counts_icho.txt} questions are based on various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova.

@@

\subparagraph{Chemical safety} 
This category comprises a total of \variable{output/question_count_per_dir/json_file_counts_safety.txt} questions, including semi-programmatically created questions covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \autocite{pubchem} (see below for details). 
Additionally, it explores crucial topics like materials' compatibility (\variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} questions) and chemical compatibility (\variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} questions), essential for understanding the hazardous impact of mixing certain materials and chemicals. 
Furthermore, it includes \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} questions based on the question bank published by the Federal/State Working Group on Chemical Safety (BLAC), which is used for the expertise examination (\enquote{Sachkundeprüfung}) according to §11 of the Chemical Prohibition Ordinance (\enquote{Chemikalien-Verbotsverordnung}).
Moreover, this category addresses questions about lab safety and topics such as pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. 
The chemical safety category stands out as one of the primary focus areas within the \chembench corpus.

@@

\subparagraph{Tool augmented models}
In addition to directly prompting \glspl{llm}, we also investigated the performance of tool-augmented systems.
For this we investigated the 7B parameter \enquote{online} model of Perplexity.AI. 
In addition, we utilized gpt-3.5-turbo as well as Claude 2, with ReAct-style tool augmentation.\autocite{yao2023react}
The latter two models had access to WolframAlpha, the ArXiv \gls{api}, a Python interpreter, as well as web search (using DuckDuckGo).
We implemented the system using Langchain with the default prompts and constrained the system to a maximum of ten \gls{llm} calls.

>>>>

To ensure that the questions do not enter a training dataset we use the same canary string as the BIG-bench project.
This requires that \Gls{llm} developers filter their training dataset for this canary string.\autocite{openai2024gpt4, srivastava2022beyond}

@@

\subparagraph{Combustion engineering}
\variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} question are based on master student examination papers at the University of Magdeburg (Germany). 
They explore topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nanomaterials}
\variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt}  questions are based on exercises from a seminar conducted at the University of Jena (Germany), delving into topics concerning functional materials and nanomaterials, exploring their properties and applications.

@@

\subparagraph{Chemistry Olympiads}
\variable{output/question_count_per_dir/json_file_counts_icho.txt} questions are based on various local and international chemistry competitions, including those held in the USA, UK, and Moldova.

@@

\subparagraph{Chemical safety} 
This category comprises a total of \variable{output/question_count_per_dir/json_file_counts_safety.txt} questions, including semi-programmatically created questions covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \autocite{pubchem} (see below for details). 
Additionally, it explores crucial topics like materials' compatibility (\variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} questions) and chemical compatibility (\variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} questions), essential for understanding the hazardous impact of mixing certain materials and chemicals. 
Furthermore, it includes \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} questions based on the question bank published by the Federal/State Working Group on Chemical Safety (BLAC), which is used for the expertise examination (\enquote{Sachkundeprüfung}) according to §11 of the Chemical Prohibition Ordinance (\enquote{Chemikalien-Verbotsverordnung}).
Moreover, this category includes questions about lab safety, pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. 
The chemical safety category stands out as one of the primary focus areas within the \chembench corpus.

@@

\subparagraph{Tool augmented models}
In addition to directly prompting \glspl{llm}, we also investigated the performance of tool-augmented systems.
For this we investigated the 7B parameter \enquote{online} model of Perplexity.AI. 
In addition, we used gpt-3.5-turbo and Claude 2 with ReAct-style tool augmentation.\autocite{yao2023react}
The latter two models had access to WolframAlpha, the ArXiv \gls{api}, a Python interpreter, as well as web search (through DuckDuckGo).
We implemented the system using Langchain with the default prompts and constrained the system to a maximum of ten \gls{llm} calls.
